\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-29 casestudies.tex
more text, updates and restructuring

\subsection{Azure Service Fabric}
\label{sec:cases:fabric}

>>>>

\subsection{Azure Service Fabric (CScale?}
\label{sec:cases:fabric}

\PDComment{I guess we should write stuff about CScale here based on our last discussion: overview of the system (collection of Fabric services connected via TPL dataflow?), of its environment (Fabric), how they interop?, why its very challenging to test? how they test currently? I am not sure if all these should go here or be split here and the experience report, we will see ... same for the above case studies}

### 2015-08-29 methodology.tex
more text, updates and restructuring

To solve this problem, and allow \psharp to be used for testing legacy distributed systems, we decided to take a radically different approach. We provide the capability to model the environment of a system using \psharp, and then allow the developer to take advantage of existing language features, such as \emph{method dispatch}, to connect the system under test with the environmental model, and finally test it using the \psharp systematic concurrency testing engine.

@@

@@

@@

\subsubsection{Using method dispatch for modeling}
\label{sec:method:model:dd}

@@

\begin{figure}[t]
\begin{lstlisting}
// Real code for detecting node expiration
public virtual bool IsNodeExpired(string node_id, DateTime expiration)
{
  return DateTime.Compare(expiration, DateTime.Now) <= 0;
}

// Mocked code for detecting node expiration
public override bool IsNodeExpired(string node_id, DateTime expiration)
{
  return this.DeletedNodes.Contains(node_id);
}
\end{lstlisting}
\vspace{-2mm}
\caption{Abstracting the node expiration logic in the Extent Manager component of Azure Storage vNext.}
\label{fig:expiration}
%\vspace{-2mm}
\end{figure}

>>>>

To solve this problem, and allow \psharp to be used for testing legacy distributed systems, we decided to take a different approach. Our approach of testing existing distributed systems using \psharp requires three key steps:

\begin{enumerate}
\item \psharp operates in the level of communicating state machines, and thus the environment of the system-under-test must be modeled using \psharp machines, while the real components of the system must be wrapped inside \psharp machines. We call this modeled environment the \psharp test harness.

\item The top level asynchrony due to message passing, has to be exposed as event sending using the \psharp runtime API. If the communication layer is not based on message passing, then additional effort must be spend into refactoring the system to use message passing. This step allows the \psharp runtime to capture and control the message passing interleavings during systematic testing.

\item Any source of nondeterminism in the system or the environment (e.g. failures and timers), must be modeled using the \psharp \texttt{Nondet()} method. This method returns a nondeterministic boolean value that is controlled by the \psharp runtime and can be used to systematically inject ``nondeterministic'' events and for bug reproduction.
\end{enumerate}

\PDComment{Step 1 and 3 are related and thus could combine, also in the following subsections I present 1 and 3 together as the process of ``modeling of environment''}

@@

We provide the capability to model the environment of a system using \psharp, and then allow the developer to take advantage of existing language features, such as \emph{method dispatch}, to connect the system under test with the environmental model, and finally test it using the \psharp systematic concurrency testing engine.

@@

\subsubsection{Test harness as \psharp state machines}
\label{sec:method:model:harness}

Draft

\subsubsection{Entry point to a \psharp test harness}
\label{sec:method:model:entrypoint}

A developer can specify the entry point of a \psharp test harness similar to how unit tests are typically written. Figure~\ref{fig:entrypoint} shows the source code of the entry point for the Azure Storage vNext \psharp test harness. The programmer can declare an entry point method using the \texttt{Microsoft.PSharp.Test} attribute. When the \psharp systematic testing engine is invoked, it will scan the binary and attempt to find a static method declared with this attribute. When such a method is found (in our example the \texttt{Execute()} method), the testing engine will invoke it and start testing the program. The systematic engine can optionally run multiple iterations of the test harness, each one potentially exploring a different schedule. In each iteration, the program state will be reset (any static fields must be explicitly reset by the programmer) and the entry point will be re-invoked.

\begin{figure}[t]
\begin{lstlisting}
[Microsoft.PSharp.Test]
public static void Execute()
{
  PSharpRuntime.CreateMachine(typeof(Environment));
}
\end{lstlisting}
\vspace{-2mm}
\caption{Static \csharp method acting as the entry point to the Azure Storage vNext \psharp test harness.}
\label{fig:entrypoint}
%\vspace{-2mm}
\end{figure}

\subsubsection{Using method dispatch for modeling}
\label{sec:method:model:dispath}

@@

@@

\begin{figure}[t]
\begin{lstlisting}
// Real code for detecting node expiration
public virtual bool IsNodeExpired(string id, DateTime time)
{
  return DateTime.Compare(time, DateTime.Now) <= 0;
}

// Mocked code for detecting node expiration
public override bool IsNodeExpired(string id, DateTime time)
{
  return this.DeletedNodes.Contains(id);
}
\end{lstlisting}
\vspace{-2mm}
\caption{Abstracting the node expiration logic in the Extent Manager component of Azure Storage vNext.}
\label{fig:expiration}
%\vspace{-2mm}
\end{figure}
